Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-20 hpmoon-asoco.tex
More addressings to @JJ and adding Julio and Jesus comments

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known
methods, suitable for dealing with large multi-objective optimization
problems. \textcolor{blue}{This paper proposes a version of these algorithms where} each island modifies a fragment of the
chromosome that encodes a possible solution to the
problem. \textcolor{blue}{The objective of this paper is} to
demonstrate that automatically setting the size of the overlapping
fragments depending on the number of islands obtains better results
than using the same size. \textcolor{blue}{This method has been
  compared} to other parallel evolutionary techniques considering a
different number of islands, chromosome sizes and benchmarks. The
analysis of the obtained experimental results, by using different
metrics, shows that our approach can provide statistically significant
improvements with respect to the base algorithm in high-dimensional,
un-decomposable, multi-objective problems. This opens a very promising
line to automatically adapt the overlapping sizes in this kind of
algorithms.

@@

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
% Pablo: ok, done in blue
\begin{bluecolor}
One of the methods that are most extensively used  to deal with
high-dimensional, multi-objective optimization problems (MOPs) are
distributed co-evolutionary algorithms \cite{Gong15models}. However,
only decomposable problems \textcolor{blue}{--that is, the ones whose  domain can be divided into subsets, calculate their partial solutions, and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
this way. A new parallel island-model evolutionary algorithm approach
\cite{Alba02Parallelism} is used here to deal with un-decomposable
problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered.}. This avoids extra steps (and
subsequent communication overhead) to recompose the complete
individuals from other islands before evaluation. 
\end{bluecolor}

%1. MOP ARE
In MOPs, several \textcolor{blue}{independent}
objectives have to be simultaneously optimized
\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
these problems the aim is to obtain a set of solutions that are better
than the rest considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
which means that there is no other solution that is equal or better
for all objectives. The objective of MOP algorithms is to find as many
solutions equally distributed in the Pareto Front as possible. In order to do that the
exploration of the search space must be very efficient, trying to
cover \textcolor{blue}{all} possible exploration paths at the same time.

@@

Usually an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} \textcolor{blue}{vector, in the case of MOPs} that describes how good the individual is
\textcolor{blue}{solving} the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

@@

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
% If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. % Why should it improve quality? - JJ Pablo: look at the 2 new paragraphs sent by Julio below (between \begin{bluecolor})
In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. \textcolor{blue}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
example of the application of the \textcolor{blue}{first alternative} was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs \textcolor{blue}{different alternatives for the recombinattion/cooperation of the subpopulations returned by worker processes}. A high
dimensional problem was used to compare these 
alternatives\textcolor{blue}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although  both papers \textcolor{blue}{described}
significant speedups, only a \textcolor{blue}{small} number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time. \textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables of the individuals in its population. Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it. Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations. In fact, different strategies to define the way to distribute the components into groups to be allocated to the available processors are required. They have been mainly defined according to three categories \cite{Jia19Coevo}: (1) static partitions of variables into groups; (2) random dynamic grouping that changes the variables among groups along the optimization process; and (3) learning-based dynamic grouping to distribute the components by applying techniques to detect the interdependence among variables along the process. }

@@

Another approach used to solve this kind of problems is the {\em
  SeLective operator Application} (SLA), presented in this paper, \textcolor{blue}{can be considered as the second alternative to evolve the individuals of a subpopulation}. In this case, each island
deals with the whole chromosome, but only modifies a fragment of it in
the crossover and mutation phase depending on the number of islands,
using the whole chromosome for fitness calculation. This allows to
deal with un-decomposable problems.

\begin{bluecolor}
 Thus, in this second alternative a suitable cooperation function must be defined to select the individuals for the new set of subpopulations. Nevertheless, the right approach would be to define an approach that makes it possible to build the right cooperation procedure to improve the convergence and convergence rate of the parallel cooperative co-evolutionary procedure with respect to the base sequential optimization procedure.

This way, the open issues are related with the searching for strategies that mathematically determine convergence rates according to the cost function and associate sampling distributions in the sequential and parallel co-evolutionary procedures including the effect of the communications providing not fully actualized components. 
\end{bluecolor}

In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
\textcolor{blue}{In that paper, it was shown}
that applying the variation operators only \textcolor{blue}{to} specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivate\textcolor{blue}{d} us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. %Again, "testing more stuff" is not a good motivation. You should try to address a specific research question that might have been raised in the previous paper - JJ
Besides comparing previous methods in this new experimental setup, in this paper 
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands \textcolor{blue}{is proposed}, comparing it with previous versions.

@@

Results also show that the relation between the number of islands
(subpopulations) and the length of the chromosome (number of decision
variables) is also a relevant factor to determine the most efficient
alternative to distributing the decision variables: the higher the
dimensionality and the overlapping, the greater the benefit of
distribution in a large number of islands. This opens up a new
challenge to be addressed in the future, by experimenting with new
ways to calculate the overlapping sizes depending on different factors
and parameters.

The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
the used methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
Then, the results of the experiments are presented (Section \ref{sec:results}), Finally, the conclusions and future work are discussed.

@@

%This is an improvement over the previous? What is the relationship? FERGU: linked
Other kind of approaches have also been explored. The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of the solutions was divided into the islands using a coordinate transformation. In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial. The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}. For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector. Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.

% Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
Addressing this kind of problems with cooperative co-evolution has
also been studied in several works with approaches closer to the one
presented here. The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality. Other authors, such as Cao et al. \cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.

@@

Giving the responsibility of different parts of the search space to
different modules, has also been explored lately by some
researchers. For example, some authors focus on the solution space
modeling the PF by dividing it into different clusters, allowing an
easily parallelizable {\em divide and conquer} approach
\citep{cheng2015adaptive}. 
Even other types of metaheuristics, 
such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
or Artificial Bee Colony Algorithm \cite{LUO2017235}, 
can rely on island models to divide the search space depending on 
the node to achieve better results.

In our previous work \citep{Garcia16hpmoon} some of
the aforementioned ideas \textcolor{blue}{were used} to compare two different dMOEAs. The first
one divided the chromosome into $P$ sections,  $P$ being the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operator application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time, both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. \textcolor{blue}{It was} discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivated us to find a new automatic method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and on this occasion, the experiments have been run on a parallel
cluster. 
Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.

@@

\subsection{Proposed methods}
In this paper \textcolor{blue}{several implemented SLA algorithms are analyzed}
 by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
Therefore, a basic distributed NSGA-II algorithm without
overlapping sections \textcolor{blue}{has been used} as the baseline (B).

@@

As in the baseline (B), an individual is migrated to another random
island after a fixed number of generations. In the new island, this
individual will be considered as one of the others in the island,
crossed and mutated in the same way, depending on the island
identifier (from 1 to $P$). Note that, unlike the other works such as the ones
described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
with complete chromosomes for fitness calculation, so our approach can
deal with decomposable and no decomposable problems.

@@

\subsubsection{Automatic SLA with overlapping islands (A)} 
As in the previous method, the sections to address by the operators are overlapped, but
instead of using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.

As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands was bigger than 8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, this
knowledge \textcolor{blue}{has been used} to propose the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.  Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.

\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandAdaptive.jpg}
\caption{Automatic SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
  $p_{th}$ and $p-c$  components (in grey) of the individuals using genetic operators (crossover and mutation). Also, every island evaluates its own individuals using the complete chromosome. After a given number of generations it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands. In this case, $c=2$.
  \label{fig:adaptive}
\end{figure*}
% --------------------------------------------------------------

Pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.

@@

% Some introduction. ... We will describe here the design of the
% experiments bla bla bla--- JJ Pablo: Done
\textcolor{blue}{In this subsection, the design of the experiments will be described, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}

% Move this to the top - JJ Pablo: Done
\textcolor{blue}{Three different quality metrics have been used in this paper. These metrics have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

\begin{itemize}
\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point. Higher values imply better quality of the PF. Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better.
\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions. As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
\end{itemize}

@@

The previously described four approaches have been run with two
different chromosome lengths ($L$): 512 and 2048. Different number of
islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
maximum number of islands has also been  used in a previous work in the
literature \cite{Martens13asynchronous}. The chosen crossover and mutation, SBX and polynomial, have also been  used previously by other
authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
% here. Has to explain - JJ
% Still not done - JJ

ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the
most widely used in this area
\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
benchmark includes several functions, with different features that are
representative of real-world optimization problems. Mathematical
formulation of each function is available in \citep{zdt2000a}. \textcolor{blue}{Please
note that the ZDT problems are non-epistatic, so in principle our
conclusions should be extensible only to multiobjective problems with
the same nature.}

The global population size is set to 1024. \textcolor{blue}{That value has been chosen} for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands. This is the minimum and maximum population size per island used by M{\"a}rtens et al. in his work \cite{Martens13asynchronous}.

>>>>

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known
methods, suitable for dealing with large multi-objective optimization
problems. \textcolor{blue}{This paper proposes a version of these algorithms where} each island modifies a fragment of the
chromosome that encodes a possible solution to the
problem. \textcolor{blue}{The objective of this paper is} to
demonstrate that automatically setting the size of the overlapping
fragments depending on the number of islands obtains better results
than using \textcolor{blue}{a fixed overlapping} size. \textcolor{blue}{This method has been
  compared} to other parallel evolutionary techniques considering a
different number of islands, chromosome sizes and benchmarks. The
analysis of the obtained experimental results, by using different
metrics, shows that our approach can provide statistically significant
improvements with respect to the base algorithm in high-dimensional,
un-decomposable, multi-objective problems. This opens a very promising
line to automatically adapt the overlapping sizes in this kind of
algorithms.

@@

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
% Pablo: ok, done in blue
\begin{bluecolor}
One of the methods that are most extensively used  to deal with
high-dimensional, multi-objective optimization problems (MOPs) are
distributed co-evolutionary algorithms \cite{Gong15models}. However,
only decomposable problems \textcolor{blue}{--that is, the ones whose  domain can be divided into subsets to calculate their partial solutions and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
this way. A new parallel island-model evolutionary algorithm approach
\cite{Alba02Parallelism} is used here to deal with un-decomposable
problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered}. This avoids extra steps (and
subsequent communication overhead) to recompose the complete
individuals from other islands before evaluation. 
\end{bluecolor}

%1. MOP ARE
In MOPs, several \textcolor{blue}{independent}
objectives have to be simultaneously optimized
\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
these problems the aim is to obtain a set of solutions that are better
than the rest considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
which means that there is no other solution that is equal or better
for all objectives. The objective of MOP algorithms is to find as many
solutions equally distributed in the Pareto Front as possible. In order to do that\textcolor{blue}{,} the
exploration of the search space must be very efficient, trying to
cover \textcolor{blue}{all} possible exploration paths at the same time.

@@

Usually\textcolor{blue}{,} an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} \textcolor{blue}{vector, in the case of MOPs} that describes how good the individual is
\textcolor{blue}{solving} the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

@@

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
% If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. % Why should it improve quality? - JJ Pablo: look at the 2 new paragraphs sent by Julio below (between \begin{bluecolor})
In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. \textcolor{blue}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
example of the application of the \textcolor{blue}{first alternative} was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs \textcolor{blue}{different alternatives for the recombination/cooperation of the subpopulations returned by worker processes}. A high
dimensional problem was used to compare these 
alternatives\textcolor{blue}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although  both papers \textcolor{blue}{described}
significant speedups, only a \textcolor{blue}{small} number of nodes were
employed (8). However, when the number of islands is increased, the division
of \textcolor{blue}{the portion of chromosome assigned to a given island} becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time. \textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables allocated to it of the individuals in its population. Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it. Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor. In fact, different strategies to define the way to distribute the components into groups to be allocated to the available processors are required. They have been mainly defined according to three categories \cite{Jia19Coevo}: (1) static partitions of variables into groups; (2) random dynamic grouping that changes the variables among groups along the optimization process; and (3) learning-based dynamic grouping to distribute the components by applying techniques to detect the interdependence among variables along the process. }

@@

Another approach used to solve this kind of problems is the {\em
  SeLective operator Application} (SLA), presented in this paper, \textcolor{blue}{can be considered as the second alternative to evolve the individuals of a subpopulation}. In this case, each island
deals with the whole chromosome, but only modifies a fragment of it in
the crossover and mutation phase depending on the number of islands,
using the whole chromosome for fitness calculation. This allows \textcolor{blue}{dealing} with un-decomposable problems.

\begin{bluecolor}
 Thus, in this second alternative, a suitable cooperation function must be defined to select the individuals for the new set of subpopulations. Nevertheless, the right approach would be to define a suitable procedure that implements an efficient cooperation strategy to improve the convergence and convergence rate of the parallel cooperative co-evolutionary procedure with respect to the base sequential optimization procedure.

This way, the open issues are related to the search for strategies that mathematically determine convergence rates according to the cost function, and associate sampling distributions in the sequential and parallel co-evolutionary procedures including the effect of the communications providing not fully actualized components. 
\end{bluecolor}

In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
\textcolor{blue}{In that paper, it was shown}
that applying the variation operators only \textcolor{blue}{to} specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivate\textcolor{blue}{d} us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. %Again, "testing more stuff" is not a good motivation. You should try to address a specific research question that might have been raised in the previous paper - JJ
Besides comparing previous methods in this new experimental setup,  
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands \textcolor{blue}{is proposed in this paper, and compared} with previous versions.

@@

Results also show that the relation between the number of islands
(subpopulations) and the length of the chromosome (number of decision
variables) is also a relevant factor to determine the most efficient
alternative to \textcolor{blue}{distribute} the decision variables: the higher the
dimensionality and the overlapping, the greater the benefit of
distribution in a large number of islands. This opens up a new
challenge to be addressed in the future, by experimenting with new
ways to calculate the overlapping sizes depending on different factors
and parameters.

The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
the \textcolor{blue}{proposed} methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
Then, the results of the experiments are presented (Section \ref{sec:results}), Finally, the conclusions and future work are discussed.

@@

%This is an improvement over the previous? What is the relationship? FERGU: linked
Other \textcolor{blue}{kinds} of approaches have also been explored. The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of the solutions was divided into the islands using a coordinate transformation. In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial. The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it \textcolor{blue}{into} processors by objective \citep{Xiao03specialized}. For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector. Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.

% Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
Many real-world problems \textcolor{blue}{require} high-dimensional data \cite{Zhang17DECAL,XU2018268}.
Addressing this kind of problems with cooperative co-evolution has
also been studied in several works with approaches closer to the one
presented here. The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality. Other authors, such as Cao et al. \cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.

@@

Giving the responsibility of different parts of the search space to
different modules, has also been explored lately by some
researchers. For example, some authors focus on the solution space
\textcolor{blue}{modelling} the PF by dividing it into different clusters, allowing an
easily parallelizable {\em divide and conquer} approach
\citep{cheng2015adaptive}. 
Even other types of metaheuristics, 
such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
or Artificial Bee Colony Algorithm \cite{LUO2017235}, 
can rely on island models to divide the search space depending on 
the node to achieve better results.

In our previous work \citep{Garcia16hpmoon} some of
the aforementioned ideas \textcolor{blue}{were used} to compare two different dMOEAs. The first
one divided the chromosome into $P$ sections,  \textcolor{blue}{with} $P$ being the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operator application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time, both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. \textcolor{blue}{It was} discovered \textcolor{blue}{in that paper} that the
performance using one or another method depends on \textcolor{blue}{both} the number of
sections \textcolor{blue}{individual's section used by each island} and the number of islands. This
motivated us to find a new automatic method to select this number of
sections of the chromosome to \textcolor{blue}{be used}, depending on the number of
islands. Besides, previous experiments were performed on a single
processor \textcolor{blue}{with a} synchronous island model and a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and \textcolor{blue}{this time}, the experiments have been run on a parallel
cluster. 
Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of \textcolor{blue}{evolving} subpopulations, and also validating the previous approach.

@@

\subsection{Proposed methods}
 \textcolor{blue}{Several implemented SLA algorithms are analyzed in this paper}
 by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
Therefore, a basic distributed NSGA-II algorithm without
overlapping sections \textcolor{blue}{has been used as the baseline option} (B).

@@

As in the baseline \textcolor{blue}{method} (B), an individual is migrated to another random
island after a fixed number of generations. In the \textcolor{blue}{destination} island, this \textcolor{blue}{new}
individual will be considered as \textcolor{blue}{one more individual in the subpopulation, being}
crossed and mutated in the same way, depending on the island
identifier (from 1 to $P$). Note that, unlike the other works such as the ones
described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
with complete chromosomes for fitness calculation, so our approach can
deal with decomposable and no decomposable problems.

@@

\subsubsection{Automatic SLA with overlapping islands (A)} 
As in the previous method, the sections \textcolor{blue}{managed} by the operators are overlapped, but
instead of using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.

As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands was bigger than 8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, this
knowledge \textcolor{blue}{has been used} to propose the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
Also, as mentioned \textcolor{blue}{before}, this is only a \textcolor{blue}{naive approximation} to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.  Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.

\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandAdaptive.jpg}
\caption{Automatic SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
  $p_{th}$ and $p-c$  components (in grey) of the individuals using genetic operators (crossover and mutation). Also, every island evaluates its own individuals using the complete chromosome. After a given number of generations\textcolor{blue}{,} it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands. In this case, $c=2$.
  \label{fig:adaptive}
\end{figure*}
% --------------------------------------------------------------

\textcolor{blue}{The} pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.

@@

% Some introduction. ... We will describe here the design of the
% experiments bla bla bla--- JJ Pablo: Done
\textcolor{blue}{The design of the experiments is described in this subsection, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}

% Move this to the top - JJ Pablo: Done
\textcolor{blue}{Three different quality metrics have been used in this paper. These metrics have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. \textcolor{blue}{The} mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

\begin{itemize}
\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point. Higher values imply better quality of the PF. Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
\item Inverted Generational Distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better.
\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions. As in \textcolor{blue}{the} previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
\end{itemize}

@@

The previously described four approaches have been run with two
different chromosome lengths ($L$): 512 and 2048. \textcolor{blue}{A} different number of
islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
maximum number of islands has also been  used in a previous work in the
literature \cite{Martens13asynchronous}. \textcolor{blue}{The chosen operators, SBX crossover and polynomial mutation, have also been  used previously by other
authors in \cite{Durillo08masterslave,CaoZLL17}, as its effectiveness has been demonstrated in this type of problems}.  % SBX is first mentioned
% here. Has to explain - JJ
% Still not done - JJ
% Pablo: Done, check if this is enough

ZDT \citep{zdt2000a} has been chosen as the benchmark, since it is the
most widely used \textcolor{blue}{one} in this area
\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
benchmark includes several functions, with different features that are
representative of real-world optimization problems. \textcolor{blue}{The} mathematical
formulation of each function is available in \citep{zdt2000a}. \textcolor{blue}{Please
note that the ZDT problems are non-epistatic, so in principle, our
conclusions should be extensible only to multiobjective problems with
the same nature.}
